The impact of environmental shocks on children's schooling in Bolivia

### 2020-05-07 full_paper_draft.Rmd
adding all of the regressions and robusteness checks

children <- subset(total_data, age < 18 & age > 4, select = c("hh_id", "age", "female", "child", "grandchild", "literacy", "dept", "rural", "attend", "reason", "register", "primary", "secondary", "floods", "droughts", "year", "job", "tasks", "money_reason", "work_reason"))

@@

reg_data <- total_subset %>%
  mutate(year_factor = as.factor(year),
         dept_factor = as.factor(dept),
         lny = log(income + 1),
         valleys = case_when(dept %in% c("Chuquisaca", "Cochahamba", "Tarija") ~ 1, TRUE ~ 0),
         mountains = case_when(dept %in% c("La Paz", "Oruro", "Potosi") ~ 1, TRUE ~ 0),
         plains = case_when(dept %in% c("Beni", "Pando", "Santa Cruz") ~ 1, TRUE ~ 0),
         flood_secondary = floods * secondary,
         drought_secondary = droughts * secondary,
         flood_pov = floods * extr,
         drought_pov = droughts * extr)

@@

#creating rural sample
rural <- subset(reg_data, rural == 1, select = c("hh_id", "id", "age", "female", "literacy", "dept_factor", "rural", "lny", "attend", "register", "floods", "droughts", "year", "child", "grandchild", "num_children", "female_hhhead", "hhhead_literacy", "hhhead_educ", "year_factor", "work_reason", "secondary", "valleys", "mountains", "plains", "dept", "extr", "flood_secondary", "drought_secondary", "flood_pov", "drought_pov"))

@@

probitMod_assist <- glm(attend ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = reg_data, family=binomial(link="probit"))

probitMod_register <- glm(register ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + primary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = reg_data, family=binomial(link="probit"))

probitMod_work <- glm(work_reason ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + primary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = reg_data, family=binomial(link="probit"))

summary(probitMod_assist)  # model summary
summary(probitMod_register)
summary(probitMod_work)
```

```{r generate probit regression table, echo = F, results = "asis"}
stargazer::stargazer(list(probitMod_assist, probitMod_register, probitMod_work), 
               title = "Full sample probit regression results", 
               label = "fullResults1",
               header = F,
               keep = c("floods", "droughts"))

@@

#example code:
#model_levels <- lm(recreation_visits ~ svr_median + svr_p10 + month_code*unit_code, data = regression_data)

#model_simple <- lm(assist ~ floods + droughts + year, data = reg_data)
#summary(model_simple)
model_assist <- lm(attend ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + rural + dept_factor + year_factor, data = reg_data)
summary(model_assist)
model_register <- lm(register ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + rural + dept_factor + year_factor, data = reg_data)
summary(model_register)
model_reason_t <- (lm(work_reason ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = reg_data))
summary(model_reason_t)

@@

```{r generate regression table, echo = F, results = "asis"}
stargazer::stargazer(list(model_assist, model_register), 
               title = "Full sample linear regression results", 
               label = "fullResults",
               header = F,
               keep = c("floods", "droughts"))
```

model_assist_r <- (lm(attend ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural))
summary(model_assist_r)
model_register_r <- lm(register ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural)
summary(model_register_r)
model_reason <- (lm(work_reason ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural))
summary(model_reason)

@@

```{r generate linear regression table rural sample, echo = F, results = "asis"}
stargazer::stargazer(list(model_assist, model_register), 
               title = "Rural sample linear regression results", 
               label = "fullResults2",
               header = F,
               keep = c("floods", "droughts"))
```

probitMod_assist_r <- glm(attend ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + child + grandchild + num_children + secondary + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural, family=binomial(link="probit"))

probitMod_register_r <- glm(register ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + child + grandchild + num_children + secondary + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural, family=binomial(link="probit"))

probitMod_work_r <- glm(work_reason ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + child + grandchild + num_children + secondary + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural, family=binomial(link="probit"))

summary(probitMod_assist_r)  # model summary
summary(probitMod_register_r)
summary(probitMod_work_r)
```

urban <- subset(reg_data, rural == 0, select = c("hh_id", "id", "age", "female", "literacy", "secondary", "dept_factor", "rural", "lny", "attend", "register", "work_reason", "floods", "droughts", "year", "child", "grandchild", "num_children", "female_hhhead", "hhhead_literacy", "hhhead_educ", "year_factor", "extr", "flood_secondary", "drought_secondary", "flood_pov", "drought_pov"))

model_assist_u <- lm(attend ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + child + grandchild + num_children + secondary + hhhead_educ + female_hhhead + dept_factor + year_factor, data = reg_data)
summary(model_assist_u)
model_register_u <- lm(register ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + child + grandchild + num_children + secondary + hhhead_educ + female_hhhead + dept_factor + year_factor, data = reg_data)
summary(model_register_u)
```

```{r linear regression generate table urban sample, echo = F, results = "asis"}
stargazer::stargazer(list(model_assist, model_register), 
               title = "Urban sample linear regression results", 
               label = "urbanlinearResults",
               header = F,
               keep = c("floods", "droughts"))

@@

probitMod_assist_u <- glm(attend ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + child + grandchild + num_children + secondary + hhhead_educ + female_hhhead + dept_factor + year_factor, data = urban, family=binomial(link="probit"))

probitMod_register_u <- glm(register ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + child + grandchild + num_children + secondary + hhhead_educ + female_hhhead + dept_factor + year_factor, data = urban, family=binomial(link="probit"))

probitMod_work_u <- glm(work_reason ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + child + grandchild + num_children + secondary + hhhead_educ + female_hhhead + dept_factor + year_factor, data = urban, family=binomial(link="probit"))

summary(probitMod_assist_r)  # model summary
summary(probitMod_register_r)
summary(probitMod_work_r)
```

>>>>

children <- subset(total_data, age < 18 & age > 4, select = c("hh_id", "age", "female", "child", "grandchild", "literacy", "dept", "rural", "attend", "reason", "register", "primary", "secondary", "floods", "droughts", "lag_floods", "lag_droughts", "year", "money_reason", "work_reason"))

@@

reg_data <- total_subset %>%
  mutate(year_factor = as.factor(year),
         dept_factor = as.factor(dept),
         lny = log(income + 1),
         valleys = case_when(dept %in% c("Chuquisaca", "Cochahamba", "Tarija") ~ 1, TRUE ~ 0),
         mountains = case_when(dept %in% c("La Paz", "Oruro", "Potosi") ~ 1, TRUE ~ 0),
         plains = case_when(dept %in% c("Beni", "Pando", "Santa Cruz") ~ 1, TRUE ~ 0),
         flood_secondary = floods * secondary,
         drought_secondary = droughts * secondary,
         flood_pov = floods * extr,
         drought_pov = droughts * extr,
         flood_lny = floods * lny,
         drought_lny = floods * lny,
         lag_flood_lny = lag_floods * lny,
         lag_drought_lny = lag_droughts * lny,
         lag_f_secondary = lag_floods * secondary,
         lag_d_secondary = lag_droughts * secondary)

@@

#creating rural sample
rural <- subset(reg_data, rural == 1, select = c("hh_id", "id", "age", "female", "literacy", "dept_factor", "rural", "lny", "attend", "register", "floods", "droughts", "year", "child", "grandchild", "num_children", "female_hhhead", "hhhead_literacy", "hhhead_educ", "year_factor", "work_reason", "secondary", "valleys", "mountains", "plains", "dept", "extr", "flood_secondary", "drought_secondary", "flood_pov", "drought_pov", "flood_lny", "drought_lny", "lag_flood_lny", "lag_drought_lny", "lag_f_secondary", "lag_d_secondary"))

@@

probitMod_assist <- glm(attend ~ floods + flood_secondary + flood_lny + droughts + drought_secondary + drought_lny + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = reg_data, family=binomial(link="probit"))

probitMod_register <- glm(register ~ floods + flood_secondary + flood_lny + droughts + drought_secondary + drought_lny + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = reg_data, family=binomial(link="probit"))

probitMod_work <- glm(work_reason ~ floods + flood_secondary + flood_lny + droughts + drought_secondary + drought_lny + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = reg_data, family=binomial(link="probit"))

@@

```{r generate probit regression table, echo = F, results = "asis"}
stargazer::stargazer(list(probitMod_assist, probitMod_register, probitMod_work), 
               title = "Full sample probit regression results", 
               label = "fullResults1",
               header = F,
               keep = c("floods", "droughts", "flood_secondary", "drought_secondary", "flood_lny", "drought_lny","age", "female", "lny", "secondary", "child", "grandchild", "num_children", "hhhead_educ", "female_hhhead"))

@@

probitMod_assist_r <- glm(attend ~ floods + flood_secondary + flood_lny + droughts + drought_secondary + drought_lny + age + female + lny + child + grandchild + num_children + secondary + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural, family=binomial(link="probit"))

probitMod_register_r <- glm(register ~ floods + flood_secondary + flood_lny + droughts + drought_secondary + drought_lny + age + female + lny + child + grandchild + num_children + secondary + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural, family=binomial(link="probit"))

probitMod_work_r <- glm(work_reason ~ floods + flood_secondary + flood_lny + droughts + drought_secondary + drought_lny + age + female + lny + child + grandchild + num_children + secondary + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural, family=binomial(link="probit"))

@@

```{r generate probit regression table rural sample, echo = F, results = "asis"}
stargazer::stargazer(list(probitMod_assist_r, probitMod_register_r, probitMod_work_r), 
               title = "Rural sample probit regression results", 
               label = "fullResults3",
               header = F,
               keep = c("floods", "droughts", "flood_secondary", "drought_secondary", "flood_lny", "drought_lny","age", "female", "lny", "secondary", "child", "grandchild", "num_children", "hhhead_educ", "female_hhhead"))

@@

urban <- subset(reg_data, rural == 0, select = c("hh_id", "id", "age", "female", "literacy", "dept_factor", "rural", "lny", "attend", "register", "floods", "droughts", "year", "child", "grandchild", "num_children", "female_hhhead", "hhhead_literacy", "hhhead_educ", "year_factor", "work_reason", "secondary", "valleys", "mountains", "plains", "dept", "extr", "flood_secondary", "drought_secondary", "flood_pov", "drought_pov", "flood_lny", "drought_lny", "lag_flood_lny", "lag_drought_lny", "lag_f_secondary", "lag_d_secondary"))

probitMod_assist_u <- glm(attend ~ floods + flood_secondary + flood_lny + droughts + drought_secondary + drought_lny + age + female + lny + child + grandchild + num_children + secondary + hhhead_educ + female_hhhead + dept_factor + year_factor, data = urban, family=binomial(link="probit"))

probitMod_register_u <- glm(register ~ floods + flood_secondary + flood_lny + droughts + drought_secondary + drought_lny + age + female + lny + child + grandchild + num_children + secondary + hhhead_educ + female_hhhead + dept_factor + year_factor, data = urban, family=binomial(link="probit"))

probitMod_work_u <- glm(work_reason ~ floods + flood_secondary + flood_lny + droughts + drought_secondary + drought_lny + age + female + lny + child + grandchild + num_children + secondary + hhhead_educ + female_hhhead + dept_factor + year_factor, data = urban, family=binomial(link="probit"))

```{r generate probit regression table urban sample, echo = F, results = "asis"}
stargazer::stargazer(list(probitMod_assist_u, probitMod_register_u, probitMod_work_u), 
               title = "Urban sample probit regression results", 
               label = "fullResults4",
               header = F,
               keep = c("floods", "droughts", "flood_secondary", "drought_secondary", "flood_lny", "drought_lny","age", "female", "lny", "secondary", "child", "grandchild", "num_children", "hhhead_educ", "female_hhhead"))

The following tables show the results with the lagged variables for floods and droughts.
```{r probit regression total sample lagged variables, echo = F, message = F}

probitMod_assist_lt <- glm(attend ~ lag_floods + lag_f_secondary + lag_flood_lny + lag_droughts + lag_d_secondary + lag_drought_lny + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = reg_data, family=binomial(link="probit"))

probitMod_register_lt <- glm(register ~ lag_floods + lag_f_secondary + lag_flood_lny + lag_droughts + lag_d_secondary + lag_drought_lny + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = reg_data, family=binomial(link="probit"))

probitMod_work_lt <- glm(work_reason ~ lag_floods + lag_f_secondary + lag_flood_lny + lag_droughts + lag_d_secondary + lag_drought_lny + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = reg_data, family=binomial(link="probit"))

```{r generate probit regression table lagged variables, echo = F, results = "asis"}
stargazer::stargazer(list(probitMod_assist_lt, probitMod_register_lt, probitMod_work_lt), 
               title = "Full sample probit regression results (lagged)", 
               label = "fullResults5",
               header = F,
               keep = c("floods", "droughts", "lag_f_secondary", "drought_f_secondary", "lag_flood_lny", "lag_drought_lny","age", "female", "lny", "secondary", "child", "grandchild", "num_children", "hhhead_educ", "female_hhhead"))

```{r probit regression rural sample lagged, echo = F, message = F}

probitMod_assist_lr <- glm(attend ~ lag_floods + lag_f_secondary + lag_flood_lny + lag_droughts + lag_d_secondary + lag_drought_lny + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural, family=binomial(link="probit"))

probitMod_register_lr <- glm(register ~ lag_floods + lag_f_secondary + lag_flood_lny + lag_droughts + lag_d_secondary + lag_drought_lny + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural, family=binomial(link="probit"))

probitMod_work_lr <- glm(work_reason ~ lag_floods + lag_f_secondary + lag_flood_lny + lag_droughts + lag_d_secondary + lag_drought_lny + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural, family=binomial(link="probit"))

```{r generate probit regression table rural sample lagged, echo = F, results = "asis"}
stargazer::stargazer(list(probitMod_assist_lr, probitMod_register_lr, probitMod_work_lr), 
               title = "Rural sample probit regression results (lagged)", 
               label = "fullResults6",
               header = F,
               keep = c("floods", "droughts", "lag_f_secondary", "drought_f_secondary", "lag_flood_lny", "lag_drought_lny","age", "female", "lny", "secondary", "child", "grandchild", "num_children", "hhhead_educ", "female_hhhead"))

```{r probit regression urban sample lagged, echo = F, message = F}

probitMod_assist_lu <- glm(attend ~ lag_floods + lag_f_secondary + lag_flood_lny + lag_droughts + lag_d_secondary + lag_drought_lny + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = urban, family=binomial(link="probit"))

probitMod_register_lu <- glm(register ~ lag_floods + lag_f_secondary + lag_flood_lny + lag_droughts + lag_d_secondary + lag_drought_lny + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = urban, family=binomial(link="probit"))

probitMod_work_lu <- glm(work_reason ~ lag_floods + lag_f_secondary + lag_flood_lny + lag_droughts + lag_d_secondary + lag_drought_lny + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = urban, family=binomial(link="probit"))

```{r generate probit regression table urban sample lagged, echo = F, results = "asis"}
stargazer::stargazer(list(probitMod_assist_lu, probitMod_register_lu, probitMod_work_lu), 
               title = "Urban sample probit regression results (lagged)", 
               label = "fullResults7",
               header = F,
               keep = c("floods", "droughts", "lag_f_secondary", "drought_f_secondary", "lag_flood_lny", "lag_drought_lny","age", "female", "lny", "secondary", "child", "grandchild", "num_children", "hhhead_educ", "female_hhhead"))

##Robustness Checks

The following results show a different income specification, the inclusion of the extreme poverty variable instead of the log of income.

```{r probit regression total sample extr, echo = F, message = F}

probitMod_assistx <- glm(attend ~ floods + flood_secondary + flood_pov + droughts + drought_secondary + drought_pov + age + female + extr + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = reg_data, family=binomial(link="probit"))

probitMod_registerx <- glm(register ~ floods + flood_secondary + flood_pov + droughts + drought_secondary + drought_pov + age + female + extr + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = reg_data, family=binomial(link="probit"))

probitMod_workx <- glm(work_reason ~ floods + flood_secondary + flood_pov + droughts + drought_secondary + drought_pov + age + female + extr + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = reg_data, family=binomial(link="probit"))

```{r generate probit regression table extr, echo = F, results = "asis"}
stargazer::stargazer(list(probitMod_assistx, probitMod_registerx, probitMod_workx), 
               title = "Full sample probit regression results (poverty measure)", 
               label = "fullResults8",
               header = F,
               keep = c("floods", "droughts", "flood_secondary", "drought_secondary", "flood_pov", "drought_pov","age", "female", "extr", "secondary", "child", "grandchild", "num_children", "hhhead_educ", "female_hhhead"))

```{r probit regression rural sample extr, echo = F, message = F}

probitMod_assist_rx <- glm(attend ~ floods + flood_secondary + flood_pov + droughts + drought_secondary + drought_pov + age + female + extr + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural, family=binomial(link="probit"))

probitMod_register_rx <- glm(register ~ floods + flood_secondary + flood_pov + droughts + drought_secondary + drought_pov + age + female + extr + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural, family=binomial(link="probit"))

probitMod_work_rx <- glm(work_reason ~ floods + flood_secondary + flood_pov + droughts + drought_secondary + drought_pov + age + female + extr + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural, family=binomial(link="probit"))

```{r generate probit regression table rural sample extr, echo = F, results = "asis"}
stargazer::stargazer(list(probitMod_assist_rx, probitMod_register_rx, probitMod_work_rx), 
               title = "Rural sample probit regression results (poverty measure)", 
               label = "fullResults9",
               header = F,
               keep = c("floods", "droughts", "flood_secondary", "drought_secondary", "flood_pov", "drought_pov","age", "female", "extr", "secondary", "child", "grandchild", "num_children", "hhhead_educ", "female_hhhead"))

```{r probit regression urban sample extr, echo = F, message = F}

probitMod_assist_ux <- glm(attend ~ floods + flood_secondary + flood_pov + droughts + drought_secondary + drought_pov + age + female + extr + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = urban, family=binomial(link="probit"))

probitMod_register_ux <- glm(register ~ floods + flood_secondary + flood_pov + droughts + drought_secondary + drought_pov + age + female + extr + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = urban, family=binomial(link="probit"))

probitMod_work_ux <- glm(work_reason ~ floods + flood_secondary + flood_pov + droughts + drought_secondary + drought_pov + age + female + extr + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = urban, family=binomial(link="probit"))

```{r generate probit regression table urban sample extr, echo = F, results = "asis"}
stargazer::stargazer(list(probitMod_assist_ux, probitMod_register_ux, probitMod_work_ux), 
               title = "Urban sample probit regression results (poverty measure)", 
               label = "fullResults10",
               header = F,
               keep = c("floods", "droughts", "flood_secondary", "drought_secondary", "flood_pov", "drought_pov","age", "female", "extr", "secondary", "child", "grandchild", "num_children", "hhhead_educ", "female_hhhead"))

The following results show the linear regression models.

model_assist_t <- lm(attend ~ floods + flood_secondary + flood_lny + droughts + drought_secondary + drought_lny + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = reg_data)

model_register_t <- lm(register ~ floods + flood_secondary + flood_lny + droughts + drought_secondary + drought_lny + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = reg_data)

model_reason_t <- (lm(work_reason ~ floods + flood_secondary + flood_lny + droughts + drought_secondary + drought_lny + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = reg_data))

```{r generate regression table, echo = F, results = "asis"}
stargazer::stargazer(list(model_assist_t, model_register_t, model_reason_t), 
               title = "Full sample linear regression results", 
               label = "fullResults11",
               header = F,
               keep = c("floods", "droughts", "flood_secondary", "drought_secondary", "flood_lny", "drought_lny","age", "female", "lny", "secondary", "child", "grandchild", "num_children", "hhhead_educ", "female_hhhead"))
```

model_assist_r <- (lm(attend ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural))
summary(model_assist_r)
model_register_r <- lm(register ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural)
summary(model_register_r)
model_reason_r <- (lm(work_reason ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural))
summary(model_reason)

```{r generate linear regression table rural sample, echo = F, results = "asis"}
stargazer::stargazer(list(model_assist_r, model_register_r, model_reason_r), 
               title = "Rural sample linear regression results", 
               label = "fullResults12",
               header = F,
               keep = c("floods", "droughts", "flood_secondary", "drought_secondary", "flood_lny", "drought_lny","age", "female", "lny", "secondary", "child", "grandchild", "num_children", "hhhead_educ", "female_hhhead"))
```

model_assist_u <- lm(attend ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + child + grandchild + num_children + secondary + hhhead_educ + female_hhhead + dept_factor + year_factor, data = urban)

model_register_u <- lm(register ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + child + grandchild + num_children + secondary + hhhead_educ + female_hhhead + dept_factor + year_factor, data = urban)

model_reason_u <- lm(work_reason ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + child + grandchild + num_children + secondary + hhhead_educ + female_hhhead + dept_factor + year_factor, data = urban)

```{r linear regression generate table urban sample, echo = F, results = "asis"}
stargazer::stargazer(list(model_assist_u, model_register_u, model_reason_u), 
               title = "Urban sample linear regression results", 
               label = "urbanlinearResults",
               header = F,
               keep = c("floods", "droughts", "flood_secondary", "drought_secondary", "flood_lny", "drought_lny","age", "female", "lny", "secondary", "child", "grandchild", "num_children", "hhhead_educ", "female_hhhead"))
